Preferences occur when you have to make a choice. Imagine you are walking on a trekking path, and you meet an intersection. At this point, two actions are possible : turn left, or turn right. Since you don't have any problem with those two actions, you can potentially do both. Suppose, in this case, that no other elements help you to determine your choice, you will chose in a non deterministic way. Now, suppose that you can read the distance from your point to your destination taking the right path or left path. Then, you will be able to chose according to the shortest path. Constraint semiring are suitable structures to define preferences and their composition. 

Soft Constraint Automata (SCA) have been developed by Arbab \& Santini \cite{Arbab2013} and constitute a solid ground to design and reason about systems with preferences. Instead of being restricted to crisp constraint, SCA defines soft constraints, based on c-semiring, and can choose the most preferred among a set of choices. Besides a choice operator, composition is also possible and results into new preferences. Defining global preferences by composition of local preferences is a design choice that we do not justify in this paper. Intuitively, the objective is to be able to remove an error of the composed automata by modifying preferences in the composite automata. A diagnosis procedure has been detailed by \cite{KAT17}. Thus, composition is at the core of the definition of Soft Constraint systems. 

Until now, several composition operators have been defined (ex: lexicographic, join). The choice of the product space must be done before composition.

In this paper, we first present the definition of a new composition framework for preferences in Soft Constraint Automata, by using the co-product. Composition is decoupled from quotient to product space. Lexicographic or join quotients are defined.

Then, the definition of a new concise model to represent, in a unified way, constraints and preferences into a semiring logic. Logic is extended to any csemiring (not only boolean csemiring). 